\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
%\usepackage[left=1in, right=2in, top=1in, bottom=1in]{geometry}

\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\abs}[1]{\left\vert#1\right\vert}

\title{Assignment1}
\date{\today}

\begin{document}
\maketitle{questions}
\begin{enumerate}
\section{vector}
\item $X$ And $Y$ are the two points with position vectors $3\overrightarrow{a}+\overrightarrow{b}$ and $3\overrightarrow{a}-\overrightarrow{b}$ respectively. write the position vector of the point $Z$ which divides the line segment $XY$ in the ratio $2:1$ externally.
\item let $\overrightarrow{a}=\hat{i}+2\hat{j}-3\hat{k}$ and $\overrightarrow{b}=3\hat{i}-\hat{j}+2\hat{k}$ be two vectors. show that the vectors $\brak{\overrightarrow{a}+\overrightarrow{b}}$ and $\brak{\overrightarrow{a}-\overrightarrow{b}}$ are perpendicular to each other.
 \item Find the vector equation of a line passing through the point $\brak{2,3,2}$ and parallel to the line $\overrightarrow{r}$=$\brak {-2\hat{i}+3\hat{j}}$+${\lambda\brak{2\hat{i}-3\hat{j}+6\hat{k}}}$. Also find the distance between the lines
 \item find the vector equation of the plane determined by the points  $A\brak{3,-1,2}$, $B\brak{5,2,4}$, $C\brak{-1,-1,6}$. Hence find the distance of the plane, thus obtained, from the origin 
 \section{Linear Forms}
 \item Find the length of the intercept, cut off by the plane $2x+y-z=5$ on the x-axis.
 \item find the coordinates of the foot of the perpendicular $Q$ drawn from $P\brak{3,2,1}$ to the plane $2x-y+z+1=0$. Also, find the distance $PQ$ and the image of the point P treating this plane as a mirror .
 \item find the value of $x$, for which the four points $A\brak{x,1,-1}$, $B\brak{4,5,1}$, $C\brak{3,9,4}$ and $D\brak{-4,4,4}$ are coplannar. 
\item A ladder $13$ m long is leaning against a vertical wall. the bottom of the ladder away from the wall along the ground at the rate of $2$ cm/sec.how fast is the height on the wall decreasing when the foot of the ladder is $5$ m away from the wall?
 \section{matrices}
 \item if $A$ is a square matrix of order $3$, with $\abs{A}=9$, then write the value of $\abs{2\cdot\text{ Adj }A}$.
 \item if $A$ and $B$ are symmetric matrices, such that $AB$ and $BA$ are both defined, then prove that $AB-BA$ is a skew symmetric matrix.
 \item using properties of determinants, find the value of $x$ for which
	\begin{align*}
	\mydet{4-x & 4+x & 4+x\\4+x & 4-x & 4+x\\4+x & 4+x & 4-x}=0
        \end{align*}
 \item using elementary row transformations , find the inverse o the matrix 
	$$\begin{bmatrix}
		2 & -3 & 5 \\
		3 & 2 & -4 \\
		1 & 1 & -2 \\
	\end{bmatrix}$$

\item using matrices, solve the following system of linear equations 
 \begin {align*}
         x+2y-3z &= -4\\
	     2x+3y+2z &= 2\\
		 3x-3y-4z &= 11\\
   \end{align*}
 \section{differentiation}
 \item From the differential equation representing the family of curves $y=\frac{A}{x}+5$, by eliminating the Orbitary constant A.
 \item if $y=\log(\cos\text{e}^x)$, then find $\dfrac{dy}{dx}$
  \item solve the fallowing differential equation:
	$\dfrac{dy}{dx}+y$ = $\cos{x}-\sin{x}$
 \item solve the differential equation 
	\begin{align*}
	   \dfrac{dy}{dx} = 1+x^2+y^2+x^2y^2,
	\end{align*}
		given that $y=1$ when $x=0$
\item Find the particular solution of the differential equation
  \begin{align*}
	\dfrac{dy}{dx}=\frac{xy}{x^2+y^2},
  \end{align*}
  given that $y=1$ when $x=0$
  \item if $X$ = $\sin t $, $Y$ = $\sin pt$, prove that $(1-x^2)\cdot \dfrac{d^2y}{dx^2}-x\cdot\dfrac{dy}{dx}+p^2y=0$.

\item differentiate $\tan^{-1} \myvec {\frac{\sqrt(1+x^2)-\sqrt(1-x^2)}{\sqrt(1+x^2)+\sqrt(1-x^2)}}$\, with respect to $\cos^{-1}{x^2}$.
\item if
 \begin{align*}
    y= (x)^{\cos x} + (\cos x)^{x}, find \dfrac{dy}{dx}
     \end{align*}
 \section{integration}
 \item find 
 	\begin{align*}
		\int_{-\dfrac{\pi}{4}}^{0}\frac{1+\tan{x}}{1-tan{x}} \, dx
         \end{align*}
         \item Find:
	\begin{align*}
		\int x \cdot \tan^{-1}{x}\,dx
	\end{align*}
\item Find : 
	\begin{align*}
l		\int \dfrac{dx}{\sqrt{5-4x-2x^2}}
	\end{align*}
 \item integrate the function 
	$\dfrac{\cos(x+a)}{\sin(x+b)}$  w $\cdot$ r $\cdot $t $\cdot x.$
 \item prove that 
	\begin{align*}
		\int_{0}^{a}f(x)dx=\int_{0}^{a}f(a-x)dx, \text{and hence evaluate} \int_{0}^{1}(x^2)(1-x)^n dx 
	\end{align*}
 \item using integration, find the area of the greatest rectangle that can be incribed in an  elipse $\dfrac{x^2}{a^2}+\frac{y^2}{b^2}$ = $1$
 \item using integration, find the area of the region bounded by the parabola $y^2$ = $4x$ and the circle $ 4x^2 + 4y^2$ = $9$.

\item using the method of integration, find the area of the region bounded by the lines $3x-2y+1$=$0$, $2x+3y-21$ = $0$ ,and  $x-5y+9$ = $0$
\section{function}
 \item let $*$ be a operator defined as :$\textbf{R}\times\textbf{R}\rightarrow\textbf{R}$ such that $a*b=2a+b,\,$a,$b\in\textbf{R}$ .Check if $*$ is a binary operation. If yes, find if it is association too.
 \item Let $A$=$R-\cbrak{2}$ and $B$ = $R-\cbrak{1}$. if $f:A \overrightarrow{} B$ is a function defined by $f\brak{x}$=$\frac{x-1}{x-2}$, show that $f$ is one-one and onto. Hence, find $f^{-1}$ 
\item show that the relation $S$ in the set $A = \cbrak{x\in Z : 0\leq x \leq 12}$ given by $S = \cbrak{(a,b):a,b\in Z,  \abs{a-b}}$ is divisible by $3$ in an equivalence relation.
\item prove that:$\cos^{-1}(\frac{12}{13})+\sin^{-1}(\frac{3}{5})$=$\sin^{-1}(\frac{56}{65})$
 \item A dietician wishes to mix two types of food in such a way the vitamin contents of the mixtures contain at least \rupee $8$ units of vitamin A and \rupee $10$ units of vitamin C. it costs \rupee $50$ per Kg to produce food I. Food II contain 1 unit/kg of vitamin C .It costs \rupee $70$ per kg to produce food II. Formulate this problem as a LPP to minimise the cost of the mixture that will produce the required diet. Also find the minimum cost.
 \section{probability}
 \item $12$ cards numbered $1$ to $12$ (one number on one end), are placed in a box and mixed up thoroughly. then a card is drawn at random from the box.If it is known that the number on the card is greater than $5$, find the probability that the card bears an odd number.
\item out of $8$ outstanding students of a school, in which there are $3$ boys and $5$ girls, a team of $4$ students is to be selected for quiz competition.find the probability that $2$ boys and $2$ girls are selected.
\item in a multiple choice examination with three possible answers with for each of the five questions, what is the probability that a candidate would get four or more correct answers just by guessing?
\item an insurance company insured $3000$ cyclists,$6000$ scooter drivers and $9000$ car drivers.the probability of an accident involving a cyclist, a scooter driver are $0.3$ , $0.5$ and $0.02$ respectively. One of the insured person meets with an accident. what is the probability that he is a cyclist ?

\end{enumerate}
\end{document}
